On finiteness of structures produced deterministically by oritatami co-transcriptional folding \thanks{This work is supported in part by KAKENHI Grant-in-Aid for Challenging Research (Exploratory) No.~18K19779 and JST Program to Disseminate Tenure Tracking System No.~6F36 granted to S.~S.}

### 2018-11-11 paper.tex
Dvipdfmx option has been causing an error
The option [dvipdfmx] causes an error so that we couldn't open paper.pdf
by Acrobat Reader. I removed them as you can see the log.
Added unary, arity 1, delta 2 case +Figures
I added the proof for delta 2, arity 1, unary. It needs some polishing still, but the main points are in there.
I also added a Fig folder with svg and png figures in case it is useful.
For the same reason, uploaded the old manuscript which has the write up for my version of the Chichen Itza construction, in case it helps Reoto

\usepackage[dvipdfmx]{color}

\usepackage[dvipdfmx]{graphicx}
\usepackage{tikz}
\usepackage{calc}

@@

>>>>

\usepackage{color}

\usepackage{graphicx}
\usepackage{tikz}
\usepackage{calc}

@@

\subsection{$\alpha = 1$, unary}

Let the point where the first transcript bead was fixed be $p$ and let $n=|\mathrm{seed}|+1$. We will argue about the situation when the first bead is stabilized outside $\hexagon_p^n$ (a hexagon of radius $n$). Let this be the $i$th bead of the transcript. Without loss of generality, we can translate the origin $(0,0)$ to the coordinates of bead $i-1$ (which is still in $\hexagon_p^n$), and we can assume that the bead outside the hexagon is fixed at $(1,1)$ (see Fig.~\ref{fig:hexagonOut}).
\begin{figure}
	\centering
	\includegraphics[width=0.3\linewidth]{./Fig/hexagonOut}
	\caption{$N_p^n$ and the position $(1,1)$ of the first bead fixed outside of it.}
	\label{fig:hexagonOut}
\end{figure}

In the elongation that places bead $i$ at $(1,1)$ there are two possibilities:
\begin{itemize}
	\item $i$ forms a bond with a bead at $(1,0)$.
	\item  $i$ does not bond to anything and $i+1$ is at $(2,1)$ bonding with a bead at $(2,0)$. If there is no bead at $(1,0)$, then placing $i$ at $(1,0)$ instead of $(1,1)$ results in the same number of bonds, leading to nondeterminism. Therefore, there has to be a bead at $(1,0)$ and it is inert, otherwise it would bond to $i$. This is analogous to case 1. below.%as in Fig.~\ref{fig:hexagonOut1}.
	\begin{figure}
		\centering
		\includegraphics[width=0.2\linewidth]{./Fig/hexagonOut1}
		%\caption{}
		\label{fig:hexagonOut1}
	\end{figure}

\end{itemize}

%The only position with which $(1,1)$ can form a bond is $(1,0)$. This means that there is a bead at $(1,0)$, which bonds to bead $i$, otherwise there are other conformations in which beads $i$ and $i+1$ add one bond to the conformation, making the behavior nondeterministic.

The next bead, $i+1$, can be fixed at $(2,1)$ or at $(0,1)$ as all other possibilities result in nondeterministic behavior immediately, so we have two cases.

\begin{enumerate}
	\item bead $i+1$ is fixed at $(2,1)$ and can bond with a bead at $(2,0)$. Now consider bead $i+2$. For $i+1$ to be fixed at $(2,1)$, $i+2$ needs to form a bond somewhere, otherwise $i+2$ could go to $(2,1)$ forming the bond with the bead at $(2,0)$ and there would be two conformations with the maximal $1$ bond. The only possibility is that there is a bead at $(3,0)$ and $i+2$ can bond with it when placed at $(3,1)$. We can apply the same argument inductively: there is some $m\geq 0$ such that grid points $(\ell,0)$ are occupied by active beads, for all $\ell\in \{2,\dots,2+m\}$, and there is no bead at $(3+m,0)$. Such an $m$ exists, and it is not greater than $n$. Then, bead $i+\ell$ is fixed at $(\ell+1,1)$ and bonds with $(\ell+1,0)$. However, bead $i+2+m$ cannot be fixed anywhere, because $i+2+m$ and $i+3+m$ can only add one bond to the conformation, and that is possible either with $i+2+m \rightarrow (2+m,1)$, $i+3+m \rightarrow (3+m,1)$ or with $i+2+m \rightarrow (2+m,2)$, $i+3+m \rightarrow (2+m,1)$. 
	\begin{figure}
		\centering
		\includegraphics[width=0.6\linewidth]{./Fig/hexagonOut2}
		\caption{}
		\label{fig:hexagonout2}
	\end{figure}

	\item bead $i+1$ is fixed at $(0,1)$. This is only possible if
	\begin{enumerate}
		\item there is an inactive bead at $(-1,0)$ and an active one at $(-2,0)$. This case is symmetrical to (1).
		\item there is no bead at $(-1,0)$, bead $i+1$ can bond with bead $i-1$ at $(0,0)$ and the bead $i+2$ can be placed at $(-1,0)$ where it can bond with $(-2,0)$, $(-2,-1)$ or $(-1,-1)$. This leads to nondeterminism, because bead $i$ at $(-1,0)$ and bead $i+1$ at $(0,1)$ has two bonds, just as the original conformation.
		\item there is a bead at $(-1,0)$ and bead $i+1$ can bond with that or with bead $i-1$ at $(0,0)$. However, this means that placing bead $i$ at $(0,1)$ at bead $i+1$ at $(1,1)$ creates the same number of hydrogen bonds, thus resulting in bead $i$ not being placed deterministically.

	\end{enumerate}
\end{enumerate}

\begin{figure}
	\centering
	%\includegraphics[width=0.3\linewidth]{./hexagonOut1}
	%\hspace{10mm} %
	\includegraphics[width=0.6\linewidth]{./Fig/hexagonOut3}

	\caption{}
	\label{fig:hexagonOut2}
\end{figure}
